### 2018-10-25 Paper/revision/reviewer_replies.tex

Comments and Questions:
\begin{enumerate}

\item \referee{P16, Figure.2,  the estimated screening parameters eq (5) based on eq(1)
quickly converge with a small number of samples (5-10 samples). It seems that
if $\mu_i$ is based on eq(1), it will still require a reasonable amount of
samples, can authors comment on why this example converges with a small number
of samples? The same question applies to Figure 5 and Figure 7.}

Convergence behavior in this case depends upon the variability in the gradient of
$G(\theta)$ with respect to individual parameters, $\theta_i$ in their respective
domains. For the numerical tests and the application considered in this work, the
gradient is not observed to vary significantly in the considered domain of the
parameters. In other words, the variance of the estimator is low. 
Hence, a small number of Monte Carlo samples are able to estimate
the screening parameters. This is a common observation in many practical
applications, and therefore the proposed methodology involving an iterative
approach can yield significant computational savings.

These points have been emphasized in the discussion in Section~6 (Summary and
Conclusion, Page 34) in the revised manuscript.

@@

\referee{
An adaptive surrogate model construction approach in reduced input parameter
space is proposed in this paper. Instead of variance based sensitivity indices,
derivative based global sensitivity measures are employed to calibration of the
important model inputs, upon which surrogate models are constructed. To
demonstrate the computational advantage, the proposed approach is then
validated against three examples.  The reviewer’s recommendation is ``major
revision''.}

Major comments:
\begin{enumerate}

\item
\referee{
In this paper, the constructed surrogate model is either a RSS or a FSS. Based
on the diagram on page 12, the resulting RSS is built upon the not sufficiently
accurate FSS model (which could lead the accuracy to decrease further), or
is the RSS constructed directly from the original model with reduced input
parameters? The diagram is ambigous on this issue.}

The reviewer correctly points out that the resulting surrogate model is either an RSS or
an FSS. However, we would like to clarify that the main purpose of the proposed
methodology is to construct an RSS based on estimates of a screening metric that
involves derivative-based global sensitivity measure (DGSM) for each uncertain parameter.
However, since estimating the metric requires model evaluations, we further exploit these
evaluations to construct an FSS (free of cost) using a sparse regression-based approach
as mentioned in the paper. Note that the FSS construction is performed simultaneously to 
ensure that the computational effort associated with obtaining converged estimates of
the screening metric and RSS construction does not overshoot that required for
constructing a sufficiently accurate FSS.

@@

The above points are already included in the paragraph on the discussion of the proposed
methodology in Section 3. Nevertheless, based on the reviewer's feedback, we have tried to
clarify and emphasize these points in the first paragraph in Section 6 (Summary and Conclusion)
in the revised manuscript.

\item
\referee{The reviewer would also like to see the comparison of the computational cost
(not just the numerical results) of DGSMs to variance based sensitivity indices
with increasing parameter dimension, e.g. Sobol’ indices incorporated with
sparse grid, since the difference decreases with increasing number of parameters.}

As suggested by the reviewer, the computational cost pertaining to the estimation of DGSM-based
sensitivity indices is compared with the cost associated with estimating the total-effect Sobol' indices
for the 19-dimensional reaction kinetics application in this work. Additionally, the comparison is 
performed for the same application with 33 uncertain rate-controlling parameters to investigate
the impact of dimensionality.

A new sub-section (5.3) on ``comparative cost analysis" has been included in the revised
manuscript.

@@

\item 
\referee{In section 4 and 5, no predictive convergence using the test data sample is
presented, only the convergence of $\epsilon_\text{LOO}$, which reuses the training data as
the validation set, is shown. This shows only the convergence of the model,
and does not necessarily indicate the (predictive) accuracy of the constructed
model, hence could lead to false conclusion. The reviewer would like to see the
convergence of $\epsilon_{L_2}$.}

As suggested by the reviewer, the plots and related discussion pertaining to the convergence 
of $\epsilon_{L_2}$ have been included for the numerical tests presented in Section 3 (Figures 3b
and 6b) and 
the chemical kinetics application presented in Section 4 (Figure 8, right).

\item 
\referee{How would the proposed approach behave when presented with severe nonlinearity
or rare events where the screening metrics could misrepresent the significance
of parameters?}

Severe non-linearity in the model output as a function of uncertain inputs could potentially lead
to a significantly large variability in its gradient. Hence, a large number of Monte Carlo samples might be
required to estimate the screening metrics with reasonable accuracy in this case depending upon the
application. Therefore, the computational effort is expected to increase in such cases. In the presence
of rare events, the variance-based approaches typically lead to inaccurate estimates of 
parametric sensitivities. Since the proposed methodology in this work aims to reduce the computational
effort pertaining to total-effect Sobol index which is a variance-based measure, it might lead to
inaccurate estimates of the screening metric and therefore to erroneous relative importance of the uncertain
inputs.

A brief discussion based on the above points has been included in the last paragraph in
Section 6 (Summary and Discussion).

\item 
\referee{The reviewer would like to see some comments on the change of computational
cost of the proposed approach with respect to the increase of parameter dimensions.}

As mentioned earlier in the response to Comment $\#$ 2, a comparative analysis of the
computational cost with increasing parameter dimensions has been included for the reaction
kinetics application in Section 5.3 in the revised manuscript. Additional comments pertaining
to the increase in computational cost and expected gains with dimensionality, based on
our findings have been included in Section 6 (Summary and Discussion).

### 2018-10-25 Paper/app.tex
..

The proposed framework in section~\ref{sec:method} is implemented to 
the H$_2$/O$_2$ reaction mechanism provided in~\cite{Yetter:1991}.
The H$_2$/O$_2$ reaction is gaining a lot of attention as a potential
source of clean energy for applications such as 
transportation~\cite{Das:1996} and fuel cell 
applications~\cite{Loges:2008,Cosnier:2016}. \rebut{We begin by providing
the necessary background information for setting up the problem
in~\ref{sub:setup}. Results and discussion based on the implementation
of the proposed framework are provided in~\ref{sub:imp}. Finally, 
in~\ref{sub:cost}, we
provide a comparative analysis of the computational cost involved
in determining relative parameter importance using DGSMs and the
total-effect Sobol index as the dimensionality increases from 19 to 33
for the present application.}

@@

Following the steps outlined in the flow-diagram in Figure~\ref{fig:flow}, model
evaluations are initially generated at $n_1$ = 5 samples. The evaluations are
used to construct a regression-based surrogate in the full-space. As
expected, the surrogate is found to be highly inaccurate. Moreover, unlike the
test problems in section~\ref{sec:examples}, we do not estimate the Sobol
total-effect sensitivity indices in the interest of following the overall framework
closely. Hence, we proceed to the screening step to estimate the screening metric
for the uncertain pre-exponents, $A_i$'s. Results are plotted below
in Figure~\ref{fig:sense_kinetics}~(top row) for both cases. Furthermore, we illustrate
the decay in the value of $\Delta\mu_s$ with iterations in 
Figure~\ref{fig:sense_kinetics}~(bottom row).

@@

In this section, we perform a comparative analysis of the computational cost
associated with obtaining converged estimates of parametric sensitivities
using DGSM, and the total-effect Sobol indices ($\mathcal{T}(\theta_i)$). The former is computed
using the parameter screening algorithm (Algorithm~\ref{alg:screen}), and the latter is
estimated analytically using a sparse-basis PCE. Note that estimating $\mathcal{T}(\theta_i)$
using a PCE has been shown to be more efficient compared to sampling techniques.
Moreover, a sparse-basis PCE is expected to require fewer training points which
enhances computational savings. To investigate the impact of the dimensionality, the
analysis is performed with 19 uncertain parameters, i.e.
the pre-exponents~($A_i$'s) as discussed earlier in~\ref{sub:setup} and~\ref{sub:imp}, and
33 uncertain parameters wherein the activation energies~($E_{a,i}$'s) are also considered to
be uncertain. The $E_{a,i}$'s are also considered to be uniformly distributed in the
interval: [$0.9E_{a,i}^\ast,1.1E_{a,i}^\ast$], where $E_{a,i}^\ast$ is the nominal value
for the $i^\text{th}$ reaction as provided in~\cite{Yetter:1991}. Note that only those
$E_{a,i}$'s with a non-zero nominal value are considered as uncertain, and therfore the
total number of uncertain parameters in the high-dimensional case is 33 as opposed to 38.

The 33-dimensional sparse basis PCE was assessed for its convergence characteristics
and its predictive accuracy using $\epsilon_{\mbox{\tiny LOO}}$~(see~\eqref{eq:loo}) and
$\epsilon_{\mbox{\tiny{L-2}}}$~(see~\eqref{eq:l2}) respectively as shown in
Figure~\ref{fig:err_samples}.  
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.45\textwidth]{./Figures/err_samples_kinetics33D}
\caption{A semi-log plot of $\epsilon_\text{\tiny LOO}$  and $\epsilon_{\mbox{\tiny{L-2}}}$
as a function of the number of training points in the 33D parameter space 
for the fuel (H$_2$)-rich case i.e. $\phi$ = 2.0. The degree of
the PCE constructed using 500 training points was found to be 3.}
\label{fig:err_samples}
\end{center}
\end{figure}
%
The sparse-basis PCEs constructed in the 19 and the 33 dimensional parameter
space are considered to have converged once $\epsilon_\text{\tiny LOO}$ is found to be
smaller than 6.0$\times$10$^{-3}$. As observed in Figures~\ref{fig:err_samples_kinetics}
and~\ref{fig:err_samples}, the number of training points required in the 19D
and the 33D cases are found to be 60 and 500 respectively. As expected, the predictive
accuracy is observed to increase with increase in the number of training points in both cases.
The estimate of $\epsilon_{\mbox{\tiny{L-2}}}$ was found to be 7.22$\times$10$^{-2}$ using the
converged 33D PCE and an independent set of model evaluations at 1000 samples.

Sensitivity estimates for the 33 uncertain parameters are hence determined
using the DGSM-based strategy and by evaluating $\mathcal{T}(\theta_i)$ analytically
using the sparse-basis PCE as discussed earlier in this section. The estimates based
on the two approaches were plotted separately and placed side-by-side for comparison
in Figure~\ref{fig:sense33D}.
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.42\textwidth]{./Figures/ub33D}
  \includegraphics[width=0.40\textwidth]{./Figures/sens_kinetics33D}
\caption{
Left: Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$) for each 
uncertain parameter, obtained using $N$ = 5, 10, 15, and 20 samples in the full parameter space.
Right: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the
semilinear elliptic PDE~\eqref{eq:semilinear}.}
\label{fig:sense33D}
\end{center}
\end{figure}
%

>>>>

The proposed framework in section~\ref{sec:method} is implemented to 
the H$_2$/O$_2$ reaction mechanism provided in~\cite{Yetter:1991}.
The H$_2$/O$_2$ reaction is gaining a lot of attention as a potential
source of clean energy for applications such as 
transportation~\cite{Das:1996} and fuel cell 
applications~\cite{Loges:2008,Cosnier:2016}. \rebut{We begin by providing
the necessary background information for setting up the problem
in~\ref{sub:setup}. Results and discussion based on the implementation
of the proposed framework are provided in~\ref{sub:imp}. Finally, 
in~\ref{sub:cost}, we
provide a comparative analysis of the computational cost involved
in determining relative parameter importance using DGSMs and the
total-effect Sobol' index as the dimensionality increases from 19 to 33
for the present application.}

@@

Following the steps outlined in the flow-diagram in Figure~\ref{fig:flow}, model
evaluations are initially generated at $n_1$ = 5 samples. The evaluations are
used to construct a regression-based surrogate in the full-space. As
expected, the surrogate is found to be highly inaccurate. Moreover, unlike the
test problems in section~\ref{sec:examples}, we do not estimate the Sobol'
total-effect sensitivity indices in the interest of following the overall framework
closely. Hence, we proceed to the screening step to estimate the screening metric
for the uncertain pre-exponents, $A_i$'s. Results are plotted below
in Figure~\ref{fig:sense_kinetics}~(top row) for both cases. Furthermore, we illustrate
the decay in the value of $\Delta\mu_s$ with iterations in 
Figure~\ref{fig:sense_kinetics}~(bottom row).

@@

In this section, we perform a comparative analysis of the computational cost
associated with obtaining converged estimates of parametric sensitivities
using DGSM, and the total-effect Sobol' indices ($\mathcal{T}(\theta_i)$). The former is computed
using the parameter screening algorithm (Algorithm~\ref{alg:screen}), and the latter is
estimated analytically by constructing a sparse-basis PCE. Note that estimating $\mathcal{T}(\theta_i)$
using a PCE has been shown to be more efficient compared to sampling 
techniques~\cite{Crestaux:2009,BlatmanSudret10}.
Moreover, a sparse-basis PCE requires fewer training points which
enhances computational savings~\cite{Sudret:2008,Blatman:2009}. 
To investigate the impact of the dimensionality, the
analysis is performed with 19 uncertain parameters, i.e.
the pre-exponents~($A_i$'s) as discussed earlier in~\ref{sub:setup} and~\ref{sub:imp}, and
33 uncertain parameters wherein the activation energies~($E_{a,i}$'s) are considered to
be uncertain in addition to the $A_i$'s. The $E_{a,i}$'s are also considered to be uniformly distributed in the
interval: [$0.9E_{a,i}^\ast,1.1E_{a,i}^\ast$], where $E_{a,i}^\ast$ is the nominal value
for the $i^\text{th}$ reaction as provided in~\cite{Yetter:1991}. Note that only those
$E_{a,i}$'s with a non-zero nominal value are considered as uncertain, and therefore the
total number of uncertain parameters in the high-dimensional case is 33 as opposed to 38.

The 33-dimensional sparse basis PCE was assessed for its convergence characteristics
and its predictive accuracy using $\epsilon_{\mbox{\tiny LOO}}$~(see~\eqref{eq:loo}) and
$\epsilon_{\mbox{\tiny{L-2}}}$~(see~\eqref{eq:l2}) respectively as shown in
Figure~\ref{fig:err_samples}.  
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.45\textwidth]{./Figures/err_samples_kinetics33D}
\caption{A semi-log plot of $\epsilon_\text{\tiny LOO}$  and $\epsilon_{\mbox{\tiny{L-2}}}$
as a function of the number of training points in the 33D parameter space 
for the fuel (H$_2$)-rich case i.e. $\phi$ = 2.0. The degree of
the PCE constructed using 500 training points was found to be 3.}
\label{fig:err_samples}
\end{center}
\end{figure}
%
The sparse-basis PCEs constructed in the 19 and the 33 dimensional parameter
space were considered to have converged once $\epsilon_\text{\tiny LOO}$ was found to be
smaller than 6.0$\times$10$^{-3}$. As observed in Figures~\ref{fig:err_samples_kinetics}
and~\ref{fig:err_samples}, the number of training points required in the 19D
and the 33D cases are found to be 20 and 500 respectively. As expected, the predictive
accuracy is observed to increase with increase in the number of training points in both cases.
The estimate of $\epsilon_{\mbox{\tiny{L-2}}}$ was found to be 7.22$\times$10$^{-2}$ using the
converged 33D PCE and an independent set of model evaluations at 1000 samples.

Before comparing the computational cost pertaining to the two approaches (DGSM-based and 
Sobol'-based) and the impact of dimensionality, we verify that the parametric sensitivities are
consistent in both cases. Sensitivity estimates for the 33 uncertain parameters obtained
using the DGSM-based strategy, and by evaluating $\mathcal{T}(\theta_i)$ analytically
using the sparse-basis PCE are plotted and placed adjacent to each other for comparison
in Figure~\ref{fig:sense33D}.
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.42\textwidth]{./Figures/ub33D}
  \includegraphics[width=0.40\textwidth]{./Figures/sens_kinetics33D}
\caption{
Left: Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$), 
obtained using $N$ = 5, 10 samples in the full parameter space; and
Right: Total-effect Sobol' indices, $\mathcal{T}(\theta_i)$ for the 33 uncertain rate-controlling
parameters ($A_i$'s and $E_{a,i}$'s).}
\label{fig:sense33D}
\end{center}
\end{figure}
%
The plots clearly indicate that the relative importance of the uncertain parameters is
consistent in both cases. Specifically, both approaches reveal that the uncertainty in
the ignition delay is predominantly due to the uncertainty in $E_{a,1}$ and $E_{a,10}$ with a 
minor contribution from $E_{a,12}$, whereas, contributions from other parameters is either zero
or negligible. These results are clearly indicative of the potential for dimension reduction in this
case using the proposed sensitivity-driven approach. A reasonably accurate RSS in a 2D
parameter space could potentially capture the uncertainty in the ignition delay due to the
uncertainty in the 33 rate-controlling parameters.

The computational cost is estimated in terms of the number of function evaluations or model runs,
denoted by $\mathcal{M}$ in each case. In the case of DGSM-based approach presented in this work, 
$\mathcal{M}$ = $N(N_p+1)$ ($N$: number of samples, $N_p$: number of parameters)
as discussed earlier in~\ref{sub:dgsm}. In the case of PCE-based computation of $\mathcal{T}(\theta_i)$,
$\mathcal{M}$ is the sum total of the number of training points used for constructing the sparse-basis
PCE and the number of evaluations used for its verification, denoted by $N_v$. In Table~\ref{tab:cost},
we provide a comparison of $\mathcal{M}$ for the two approaches in the case of 19 and 33 uncertain
parameters for the H$_2$/O$_2$ reaction kinetics application. 
%
\begin{table}[htbp]
\renewcommand{\arraystretch}{1.5}
\caption{A comparison of computational cost for the DGSM-based and Sobol'-based parametric 
sensitivity analysis in the case of 19 and 33 uncertain rate-controlling parameters.}
\begin{center}
\begin{tabular}{c|c|c|}
\cline{2-3}
& \multicolumn{2}{ c| }{$\mathbf{\#}$ \textbf{of Function Evaluations/Model Runs}~($\mathcal{M}$)} \\ \cline{2-3} 
& \textbf{19D} & \textbf{33D} \\  \hhline{===}
\multicolumn{1}{ |l|| }{\textbf{DGSM-based}, $\widehat{\mathcal{C}_i\mu_i}$} & 5(19+1) = 100 & 5(33+1) = 170 \\ 
\cline{1-3}
\multicolumn{1}{ |l|| }{\textbf{Total-effect Sobol'}, $\mathcal{T}(\theta_i)$} & 20 + $N_v$ & 
500 + $N_v$ \\ \cline{1-3}  
\end{tabular}
\end{center}
\label{tab:cost}
\end{table}
%
For the 19D case, estimating the converged estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$)
required 5 samples. However, since finite difference was used in this work for estimating the gradient of the
model output, a total of 100 model runs were required. However, as mentioned earlier in~\ref{sub:dgsm}, depending
upon the application, it is possible to explore efficient techniques for gradient estimation such as those involving 
adjoint computation and automatic differentiation. Hence, there is scope for reduction in the computational cost
associated with the DGSM-based approach. Constructing the sparse-basis PCE requires only 20 samples in
the 19D parameter space with uncertain pre-exponents. However, additional model runs typically ranging from
$\mathcal{O}(10^{2})$ - $\mathcal{O}(10^{3})$ are needed to build a cross validation test suite to verify the 
accuracy of the PCE. The DGSM-based approach could thus yield computational gains especially when 
efficient gradient computation techniques are used. The comparison is significantly more favorable for the 
proposed DGSM-based framework in the higher dimensional case involving 33 uncertain parameters. 
Once again, converged estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$) are obtained
using only 5 samples in the 33D parameter space. Hence, a total of 170 model runs are needed in this case
including for gradient computation using finite difference. Whereas,
constructing the sparse PCE itself requires model runs at 500 training points to sufficiently converge. Additional
model runs are required to further verify the accuracy of the resulting PCE. Note that the analysis was performed
for the fuel-rich case. However, similar trends are expected for the fuel-lean case and we do not include them here
for brevity.

In addition to the potential for computational cost reduction using the proposed framework, the comparative 
analysis also reveals the significant increase in computational effort pertaining to the estimation of the total-effect
Sobol' indices as the dimensionality increases from 19 to 33 despite using an efficient approach involving
sparse-basis PCEs. It can thus be understood that for higher dimensional problems involving hundreds of 
parameters, conventional approaches can quickly become prohibitive and the proposed framework could help
reduce the computational effort by several orders of magnitude.

### 2018-10-25 Paper/disc.tex
..

Parameter screening methodology was implemented to low-to-moderate dimensional
test problems and an accurate RSS was constructed to demonstrate potential for
computational gains in each case. Furthermore, the overall framework was
implemented  to a relatively higher dimensional application involving kinetics
of the H$_2$/O$_2$ reaction mechanism.  Significant dimension reduction (19 
dimensions to 3 or 4 dimensions) was
accomplished for two different scenarios involving a fuel-rich and a fuel-lean
mixture. In both cases, the resulting RSS was able to capture the input-output
relationship as well as the uncertainty in the quantity of interest with
reasonable accuracy. Additional highlights of the proposed framework are as
follows:
\begin{enumerate}
\item Although PCEs were used in this work, the proposed framework is
agnostic to the choice of the surrogate model construction method.
%\item The quantity of interest must be differentiable with respect to each uncertain parameter
%for the derivative-based sensitivity measures in~\eqref{eq:mu} to be defined. 
%to ensure accurate estimation of the derivative-based sensitivity measures in~\eqref{eq:mu}.
\item Substantial computational gains are expected in situations involving
compute-intensive simulations even if the scope for dimension reduction is
small. 
%Hence, careful judgment pertaining to the construction of a reduced-order
%surrogate as well as resource allocation is needed. is required when
%implementing the framework.

>>>>

Parameter screening methodology was implemented to low-to-moderate dimensional
test problems and an accurate RSS was constructed to demonstrate potential for
computational gains in each case. Furthermore, the overall framework was
implemented  to a relatively higher dimensional application involving kinetics
of the H$_2$/O$_2$ reaction mechanism.  Significant dimension reduction (19 
dimensions to 3 or 4 dimensions) was
accomplished for two different scenarios involving a fuel-rich and a fuel-lean
mixture. In both cases, the resulting RSS was able to capture the input-output
relationship as well as the uncertainty in the quantity of interest with
reasonable accuracy. \rebut{Moreover, it was shown that the parameter
screening procedure (Algorithm~\ref{alg:screen}) was able to determine the
relative importance of the
parameters using only 5 samples in an even higher dimensional
case involving 33 uncertain rate-controlling parameters. It was observed that
the parameter dimension could be reduced from 33 to 2 in this case.}
Additional highlights of the proposed framework are as follows:
\begin{enumerate}
\item Although PCEs were used in this work, the proposed framework is
agnostic to the choice of the surrogate model construction method.
%\item The quantity of interest must be differentiable with respect to each uncertain parameter
%for the derivative-based sensitivity measures in~\eqref{eq:mu} to be defined. 
%to ensure accurate estimation of the derivative-based sensitivity measures in~\eqref{eq:mu}.
\item Substantial computational gains are expected in situations involving
compute-intensive simulations even if the scope for dimension reduction is
small. \rebut{However, computational gains using the proposed framework
are expected to increase significantly with the increase in dimensionality of the
parameter space.}
%Hence, careful judgment pertaining to the construction of a reduced-order
%surrogate as well as resource allocation is needed. is required when
%implementing the framework.

### 2018-10-25 Paper/examples.tex
..

\begin{figure}[htbp]
 \begin{center}
 \begin{tabular}{cc}
  \includegraphics[width=0.45\textwidth]{./Figures/err_samples_borehole}
  &
  \includegraphics[width=0.45\textwidth]{./Figures/errL2_samples_borehole}
  \\ (a) & (b)
  \end{tabular}
  \includegraphics[width=0.45\textwidth]{./Figures/pdf_comp_borehole}
  \\ (c)
\caption{(a) A comparison of order of the leave-one-out-error 
($\epsilon_{\mbox{\tiny{LOO}}}$) as a function of number of regression samples
used for constructing the PCE in 4, 5, and 7 dimensions. \rebut{The degree of
the PCE using 50 training points was found to be 3, 2,and 2 in the 4D, 5D, and 7D case respectively;
(b) Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$) 
for the PCEs constructed in 4D, 5D, and 7D};
and (c) A comparison of
PDFs of the discharge, $\mathcal{Q}$, generated using 10$^{6}$ samples from
the marginal distributions of the uncertain parameters in each case.} 
\label{fig:conv_bore}
\end{center}
\end{figure}
%
As expected, it is observed that the PCE constructed in the 4D space converges
at a much faster rate. For instance, if a PCE with $\mathcal{O}(10^{-4})$
accuracy is sought, we need function evaluations at only about 50 sample points
in the 4D parameter space whereas the number of samples needed in the full 7D
space seems much higher. Latin hypercube sampling (LHS) was used in
each case. It must be pointed out that the error in Figure~\ref{fig:conv_bore}(a)
is not expected to decrease monotonically with the increase in sample size
owing to the penalty term in the regularized optimization problem in Eq.~\ref{eq:reg}. 
\rebut{However, the plot of $\epsilon_{\mbox{\tiny{L-2}}}$ as a function of sample
size for the three surrogate models in Figure~\ref{fig:conv_bore}(b)
clearly demonstrates the trade-off between
computational effort associated with surrogate construction and its predictive 
accuracy. For a small sample size of 20, the relative  error in the case of 4D
PCE is found to be the smallest. However, as the sample size increases, the higher
order PCE becomes more accurate. Note that the same set of 50 samples in the
validation test suite were used in each case. Hence, when limited computational resources
are available, the proposed methodology could yield substantial gains due to fast
convergence as well as higher accuracy of the surrogate in the reduced space.
The gains are expected to increase exponentially as the dimensionality of the 
input space increases.}

@@

%We note that the total Sobol sensitivity indices are in excellent agreement

@@

We computed converged estimates of the Sobol

@@

\rebut{The comparison of convergence characteristics of $\epsilon_{\mbox{\tiny{L-2}}}$
illustrated in Figure~\ref{fig:conv_elliptic}(b) indicates that for a small sample size of 20,

@@

be slightly more accurate. However, the order of the accuracy is found to be 

@@

Once again, we verify the accuracy of the RSS by estimating $\epsilon_{\mbox{\tiny{L-2}}}$
using model evaluations at 1000 independent MC samples in the 10D parameter
space. The RSS was found to be accurate
within 5$\%$. In order to bolster confidence in the RSS, we compare PDFs of the QoI
as well as a normalized histogram plot based on sparse model evaluations in the  
validation test-suite, in 
Figure~\ref{fig:conv_elliptic}(c). While the two PDFs are in favorable agreement,
the modal estimate and the spread in the QoI based on the histogram is also captured
by them. Hence, the RSS could be used with a reasonable degree of confidence to
quantify the uncertainty in $\mathcal{F}(\vec\theta)$ thereby leading to
a computational advantage in this case.

>>>>

\begin{figure}[htbp]
 \begin{center}
 \begin{tabular}{cc}
  \includegraphics[width=0.45\textwidth]{./Figures/err_samples_borehole}
  &
  \includegraphics[width=0.45\textwidth]{./Figures/errL2_samples_borehole}
  \\ (a) & (b)
  \end{tabular}
  \includegraphics[width=0.45\textwidth]{./Figures/pdf_comp_borehole}
  \\ (c)
\caption{(a) A comparison of order of the leave-one-out-error 
($\epsilon_{\mbox{\tiny{LOO}}}$) as a function of number of regression samples
used for constructing the PCE in 4, 5, and 7 dimensions. \rebut{The degree of
the PCE constructed using 50 training points was found to be 
3, 2,and 2 in the 4D, 5D, and 7D case respectively;
(b) Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$) 
for the PCEs constructed in 4D, 5D, and 7D};
and (c) A comparison of
PDFs of the discharge, $\mathcal{Q}$, generated using 10$^{6}$ samples from
the marginal distributions of the uncertain parameters in each case.} 
\label{fig:conv_bore}
\end{center}
\end{figure}
%
As expected, it is observed that the PCE constructed in the 4D space converges
at a much faster rate. For instance, if a PCE with $\mathcal{O}(10^{-4})$
accuracy is sought, we need function evaluations at only about 50 sample points
in the 4D parameter space whereas the number of samples needed in the full 7D
space seems much higher. Latin hypercube sampling (LHS) was used in
each case. It must be pointed out that the error in Figure~\ref{fig:conv_bore}(a)
is not expected to decrease monotonically with the increase in sample size
owing to the penalty term in the regularized optimization problem in Eq.~\ref{eq:reg}. 
\rebut{However, the plot of $\epsilon_{\mbox{\tiny{L-2}}}$ as a function of sample
size for the three surrogate models in Figure~\ref{fig:conv_bore}(b)
clearly demonstrates the trade-off between
computational effort associated with surrogate construction and its predictive 
accuracy. For a small sample size of 20, the relative  error in the case of 4D
PCE is found to be the smallest. However, as the sample size increases, the higher
order PCE becomes more accurate. Note that the same set of 50 samples in the
validation test suite were used in each case. Hence, when limited computational resources
are available, the proposed methodology could yield substantial gains due to fast
convergence as well as higher accuracy of the surrogate in the reduced space.
The gains are expected to increase exponentially as the dimensionality of the 
input space increases.}

@@

%We note that the total Sobol' sensitivity indices are in excellent agreement

@@

We computed converged estimates of the Sobol'

@@

\rebut{The comparison of predictive accuracy of the PCEs using $\epsilon_{\mbox{\tiny{L-2}}}$
is illustrated in Figure~\ref{fig:conv_elliptic}(b). It is observed that for a small sample size of 20,

@@

be slightly more accurate although the order of the accuracy is found to be 

@@

Using model evaluations at 1000 independent MC samples in the 10D parameter
space, the RSS was found to be accurate
within 5$\%$. In order to bolster confidence in the RSS, we compare PDFs of the QoI
as well as a normalized histogram plot based on sparse model evaluations in the  
validation test-suite, in 
Figure~\ref{fig:conv_elliptic}(c). While the two PDFs are in favorable agreement,
the modal estimate and the spread in the QoI based on the histogram is also captured
by them. Hence, the RSS could be used with a reasonable degree of confidence to
quantify the uncertainty in $\mathcal{F}(\vec\theta)$ thereby leading to
a computational advantage in this case.
